A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-18 paper.tex
Corrected
closes #9
Done: Preliminaries

Application of intuitionistic fuzzy sets, bacillus colonies
recognition \cite{davarzani2013novel}

Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}

intuitionistic inference engine \cite{cornelis2001compositional} %Que
                                %diferencias hay?
%% (Amaury): oh, sí voy a poner las diferencias. Nomás puse todo esto
%% para acordarme :D

implementation of a ifis, castillo \cite{castillo2007intuitionistic}
% Por?  
%% (A): Porque es lo más cercano a un FIS mamdani intuicionista. al
%% menos de lo que encontré.

more inference \cite{bustince1995method}

centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
%% Porque yo propongo una fórmula para calcular centroide de un IFS, y
%% como la competencia de un IFS sería un fuzzy set tipo 2, iba a
%% hablar un poco de eso

and even more inference \cite{marinov2005method}

Intuitionistic control washing machines \cite{akram2014intuitionistic}

@@

Define in more detail intuitionistic fuzzy sets.

Formulas and basic explanation (below) \cite{atanassov2013intuitionistic}

% intuitionistic fuzzy set
\begin{equation}
  A^{*} = \{\langle x, \mu _{A} (x), \nu _{A} (x) \rangle | x \in E\}
\end{equation}

@@

@@

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdany %% (A): ahhhhh cierto, cierto
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

>>>>

A goal of this work is to propose a method to design a Mamdani IFIS that is
similar in construction to the traditional Mamdani FIS. There are works
that have successfully constructed inference engines that use IFS
instead of traditional FS, but most of these works are not Mamdani
systems. Another goal is to fully integrate the concept of
non-membership into the inference process in a meaningful way,
considering how the non-membership concept should affect the process.

A straightforward method to obtain an inference by using IFS is to
apply the implication operator over a number of IFS. This operator,
proposed by K. T. Atanassov, is described in
\cite{atanassov2013intuitionistic} as in (\ref{ifs-implication})

% intuitionistic fuzzy set
\begin{equation}
  \label{ifs-implication}
  \begin{aligned}
  A \implies B = & \{ \langle x, max(\nu_{A} (x), \mu_{B}(x)),\\
  &\quad min(\mu_{A} (x), \nu_{B} (x)) \rangle | x \in E \}
\end{aligned}
\end{equation}

C. Cornelis and G. Deschrijver \cite{cornelis2001compositional}
generalize the Compositional Rule of Inference to IFSs
%intuitionistic inference engine \cite{cornelis2001compositional} %Que
                                %diferencias hay?

A method for inference in approximate reasoning based on normal
intuitionistic fuzzy sets \cite{bustince1995method}

A Method and Electronic Circuit for Intuitionistic Fuzzy Inference
\cite{marinov2005method}
An intuitionistic fuzzy system for time series analysis in plant
monitoring and diagnosis \cite{castillo2007intuitionistic}

% Applications
Intuitionistic fuzzy sets in some medical applications
\cite{szmidt2001intuitionistic}
Switching between type-2 fuzzy sets and intuitionistic fuzzy sets: an
application in medical diagnosis \cite{own2009switching}
Intuitionistic preference relations and their application in group
decision making \cite{xu2007intuitionistic}
An application of intuitionistic fuzzy information for handwritten
Arabic word recognition \cite{baccour2008application}
Application of intuitionistic fuzzy sets, bacillus colonies
recognition \cite{davarzani2013novel}

% Por?  
%% (A): Porque es lo más cercano a un FIS mamdani intuicionista. al
%% menos de lo que encontré.

%%%%%%%%Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}

%%%%%%%%centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
%% Porque yo propongo una fórmula para calcular centroide de un IFS, y
%% como la competencia de un IFS sería un fuzzy set tipo 2, iba a
%% hablar un poco de eso

@@

An IFS, as defined by K. T. Atanassov in
\cite{atanassov2013intuitionistic}, is usually represented by a
capital letter (as a traditional set) and an uppercase star,
e.g. $A^{*}$. The definition for an IFS is expressed in
(\ref{ifs-definition}), where $x$ is an element of the set,
$\mu_{A}(x)$ is the membership for that element in the set, and
$\nu_{A}(x)$ is the non-membership for that element in the set. For
every element in an IFS, the interval defined in
(\ref{intuitionistic-interval}) must be satisfied. If for every
element in an IFS $\mu_{A}(x) + \nu_{A}(x)$ is equal to 1, then this
IFS represents an ordinary fuzzy set, and it is defined by
(\ref{ifs-form}).

% intuitionistic fuzzy set
\begin{equation}
  \label{ifs-definition}
  A^{*} = \{\langle x, \mu _{A} (x), \nu _{A} (x) \rangle | x \in E\}
\end{equation}

@@

If for a given IFS $\mu_{A}(x) + \nu_{A}(x) < 1$, then the concept of
indeterminacy (also found in the literature as non-determinacy and
hesitancy) arises. Indeterminacy can be described as the
uncertainty about the uncertainty, or how certain one can be about the
membership of an element in a given set. This can be confused by the
footprint of uncertainty (FOU) found in T2-FS, which could also be
described as the uncertainty about the uncertainty, but in this case,
the FOU represents a set of values that the membership of an element
in a given T2-FS is taking. For example, one could add indeterminacy
to a T2-FS, and the indeterminacy would represent how certain or
uncertain is the FOU in the T2-FS. For every element $x$, the
indeterminacy $\pi$ is defined as in (\ref{fs-as-ifs-if}).

@@

% Ya lo menciono en el método propuesto

% Lastly, in the proposed method, the intuitionistic membership
% functions (IMF) representing the consequents need to be
% aggregated. This aggregation can be done by applying the union
% operator over the different IFS. This operator is defined in
% \ref{atanassov2013intuitionistic} as in (\ref{ifs-union}).

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).
